### 2022-06-14 paper.tex
mention PyPI

\texttt{scbs} is free and open source, and the package can be installed via the Python package manager. The source code and the package are available at \href{https://github.com/LKremer/scbs}{https://github.com/LKremer/scbs}, where we also provide detailed documentation including a tutorial that demonstrates a complete \texttt{scbs} analysis on an example data set.

>>>>

\texttt{scbs} is free and open source.
The package is available on the Python Package Index (PyPI) and can be installed with the Python package installer pip.
The source code is hosted at \href{https://github.com/LKremer/scbs}{https://github.com/LKremer/scbs}, where we also provide detailed documentation including a tutorial that demonstrates a complete \texttt{scbs} analysis on an example data set.
